---
title: Maximising Profits for Broadway Theatres
author: team
output: github_document
---

```{r, message = FALSE, echo = FALSE}
library(tidyverse)
library(broom)
library(tidytuesdayR)
library(knitr)
library(tidymodels)
library(palmerpenguins)
```

## Summary

Gross revenue is important to brands and companies as it directly reveals whether income outweighs expenses and affects sellers’ decision on whether to continue this transaction. Therefore, finding ways to maximize gross revenue is necessary for a long lasting company. In this project, we focus on Broadway musicals weekly grosses (weekly box office gross for all shows). Comparing weekly gross in various theaters, we plan to explore factors that attribute to different amount of revenue and how they are related to each other.

Our research topic is: How to maximize revenues for Broadway theaters? 

The dataset used comes from Playbill, which is a US magazine for theatre-goers. The information of weekly box office grosses comes from 'The Broadway League', an association for Broadway theatres. 

There are 47,524 observations of shows included at different times of the year. 
There are 14 variables. Some of the more important ones which we will be using in our analysis include the following:

1. `weekly_gross`
2. `avg_ticket_price`
3. `seats_sold`
4. `seats_in_theatre`
5. `pct_capacity`
6. `performances`

```{r load-data, echo = FALSE, message = FALSE, warning = FALSE}
grosses <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-28/grosses.csv', guess_max = 40000)
```

Initially, we wanted to look at how average ticket price could be impacted by the different variables as well, but we realised that there was no clear relationship that could be concluded. Thus, to increase the depth of our analysis, we decided to focus on gross revenue instead, specifically on how average ticket price can impact gross revenue. 

Our hypothesis is:
Theatre's weekly gross revenue is affected by average ticket price, theatre size, percentage of seats capacity sold, number of weeks being run, and number of performances in the week. Specifically, larger theatre size, higher average ticket price, higher percentage of seats capacity sold, higher number of performances in the week, and lower number of weeks the performance was showing attribute to higher weekly gross revenue.

We created various visualizations, generated a model, and applied inferential statistics to aid us in our investigation. Here is a summary of the following graphs we found useful and included in our presentation:

### Mutation of `theatre_size`
Since “percentage of seat capacity sold” may be a factor affecting weekly gross and differs depend on total seats in theater, we first drew a density graph to see how “seat capacity” is distributed. As the graph reveals, the seat capacity varies between different theaters. The size of a theatre might be a factor which influences the relationship between variables. Therefore, we mutated the theatres into “large”, “medium”, and “small” using numbers based on the distribution we see in the density graph. 

### Frequency of Weekly Gross Revenue
As a preliminary visualisation to better understand the data, two different versions of this graph were incorporated. The first was a simple black-and-white one, where we see the distribution is right-skewed, with most shows earning approximately $0.5 million per week. Only a few shows manage to earn above $3 million, and that might be considered special occasions such as finale or opening weeks, where there is a surge in demand. 
 
The second version was completed after a mutation to the dataset was complete, where we divided theatres into small, medium, or large. Within the graph, we can see that small theateres generally earn less revenue due to less seats being sold, as opposed to large theatres. Large theatres, as shown in the visualisation, tends to have a higher probability of being able to earn more. The peak of the different theatre sizes seems to earn higher and higher revenue, the larger they are. This suggests that indeed, one of the factors that affect weekly gross revenue is the theatre size.

### Percentage of Seats Capacity Sold and Weekly Gross Revenue:
We plotte a scatter plot for the visualization of “weekly gross revenue" vs. “percentage of seats capacity sold” and mapped colours according to theatre size. The plot reveals the fact that higher percentage of seats capacity sold leads to higher weekly gross revenue. Besides, we find that even under same percentage, theatres with larger size will have higher weekly gross revenue. This is the same as we expected, since the total number of seats is higher in larger theatres.

### Week Running and Weekly Gross Revenue:
We thought that total number of weeks the show is being run might be a factor. However, because there wasn't such a variable in our data, we mutated and counted different shows. We also had to separate out same shows that were being played in different theatres. However, as we visualised it in a scatter plot, there is no clear relationship. It seems to be completely random, hence, the weeks running of the show is not a factor of weekly gross revenue. 

### Number of Performances in the Week and Weekly Gross Revenue:
We then use geom_jitter for the plot of “weekly gross revenue” vs. “number of performances in the week”. However, the graph doesn’t indicate any relationship between them since the data are randomly disbributed without any pattern (that is, theatres with low number of performances per week can have high weekly revenue, while those with high number of performances per week may receive revenue not as high). This is the same for the relationship between “number of performances in the week” and “average ticket price”.

### Main Research: Average Ticket Price and Weekly Gross Revenue
In the graph to graph average ticket price with weekly gross revenue, the initial points seem to go up linearly, but then come down, suggesting an exponential relationship, as seen below.

```{r main-question, message = FALSE, warning = FALSE, echo = FALSE, cache = TRUE}
grosses %>%
  ggplot(aes(y = weekly_gross,x = avg_ticket_price)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(title = "Average Ticket Price vs Weekly Gross Revenue",
       x = "Average Ticket Price",
       y = "Weekly Gross Revenue") +
  scale_y_continuous(labels = label_dollar(suffix = "M", scale = 1e-6))
```

Economically, the graph makes sense. Average ticket prices increasing would increase gross revenue logically. However, at a certain point as price continues increasing, the demand becomes price inelastic, which means the consumers become more reluctant to buy the tickets due to high price, so the seats sold drops, resulting in lower gross revenue at high prices. 

To see if this was indeed the case, we plotted a graph between seats sold and average ticket price. As you can see with the graph in our presentation, there are several red points, where price > 400. Below this threshold, it seems consumers do not really mind the price, they would still be willing to buy it, suggesting that they have relatively price inelastic demand. However, above 400, consumers seem to be more reluctant to buy the tickets. Surprisingly, these shows are all played in medium sized theatres, rather than small ones, where one would expect price to be larger due to higher demand. 

Going back to the initial graph, we decided a log-log model might be the best, and hence we mutated a new value to take the logs of weekly gross revenue and average ticket price. However, before we did that, we had to add 0.0001 to each point since there were observations with values of 0 for both variables, then we plotted a graph to make sure we could indeed use linear model regression. 

We set the linear regression model, splitting our data into testing and training, whilst creating a recipe and workflow, and was able to derive the R squared and RMSE values for testing and training data, which we found to be relatively similar. Both the R squared and RMSE value is similar for both training and testing data.

Here is the mathematical equation that we derived from the model: $$y=e^{6.81}x^{1.51}$$

### Conclusion:
Among the variables we investigated, we found that theatre size, percentage capacity, and average ticket price influenced weekly gross revenue of shows, whereas neither the number of weeks the performance was showing nor the number of performances in a week had an effect. The relationship modelled between average ticket price and weekly gross revenue was quite successful as we found a relatively accurate model. 

The result proves some of our hypothesis. It reveals that to maximize theatre's gross revenue, the theatre size needs to be larger, with a high percentage of seats capacity sold each show, and a medium average ticket price that is neither too high or too low.

Some limitations we faced with this data could likely be the geography, because it is limited to Broadway only, which could only be applicable to a certain set of customers. The data set size is also a limitation. 

As an extension, we could hopefully find another model in the future that would be able to consider the curvature of the graph, making a more accurate model, since the log models do not encompass that section of the graph. We could also investigate why there are values of 0 for average ticket prices for some shows. 

## Presentation

Our presentation can be found [here](http://rpubs.com/JeniLiu/presentation).

Our pre-recorded video can be found [here](https://media.ed.ac.uk/media/IDS+2021-2022+PresentationA+team/1_ac93sfh1).

## Data 
Hughes, E. & Mock, T. (2018, April 28), Broadway weekly grosses, <https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-04-28>

See http://libraryguides.vu.edu.au/c.php?g=386501&p=4347840 for guidance on proper citation for datasets. 
If you got your data off the web, make sure to note the retrieval date.

## References
Hughes, E. & Mock, T. (2018, April 28), Broadway weekly grosses, <https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-04-28>
