---
title: Maximising Profits for Broadway Theatres
author: team
output: github_document
---

```{r, message = FALSE, echo = FALSE}
library(tidyverse)
library(broom)
library(tidytuesdayR)
```

## Summary

Gross revenue is important to brands and companies as it directly reveals whether income outweighs expenses and affects sellers’ decision on whether to continue this transaction. Therefore, finding ways to maximize gross revenue is necessary for a long lasting company. In this project, we focus on Broadway musicals weekly grosses (weekly box office gross for all shows). Comparing weekly gross in various theaters, we plan to explore factors that attribute to different amount of revenue and how they are related to each other.

Our main research topic is: How to maximize profits for Broadway theaters?

The dataset used comes from Playbill, which is a US magazine for theatre-goers. The information of weekly box office grosses comes from 'The Broadway League', an association for Broadway theatres. 

There are 47,524 cases of shows that are being played in the theatres at different times in a year.
There are 14 variables. Some of the more important ones which we will be using in our analysis include the following:

1. `show`
2. `theatre`
3. `weekly_gross`
4. `avg_ticket_price`
5. `seats_sold`
6. `seat_capacity`
7. `pct_capacity`
8. `performances`

```{r load-data, echo = FALSE}
grosses <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-28/grosses.csv', guess_max = 40000)
```

In this dataset, we have variables such as “average ticket price”, “percentage of seat capacity sold”, and “number of performances in the week”, which may affect weekly gross revenue. Further, we think the variables “seat capacity” and “number of weeks being run” may have an influence on “average ticket price”. Therefore, our research questions are:

1.What are the factors that affect weekly gross revenue?

2.What are the factors that affect average ticket price of a show, and how average ticket price influence the weekly gross revenue earned?

Our hypotheses are:

1.Higher “average ticket price”, “percentage seats capacity sold”, and “number of performances in the week week” lead to higher “weekly gross revenue.”

2.More specifically, higher “seat capacity” and “number of weeks being run” can lead to higher “average ticket price”.

We plan to create various visualizations with models and apply inferential statistics to find out the relationship between those variables.

Since “percentage of seat capacity sold” may be a factor affecting weekly gross and differs depend on total seats in theater, we first draw a density graph to see how “seat capacity” is distributed. As the graph reveals, the seat capacity varies greatly in different theaters. The size of a theatre might be a factor which influences the relationship between variables. Therefore, we mutate the theatres into “large”, “medium”, and “small” based on theatre size and do visualizations to further explore the relationship.

First we look at factors that affect weekly gross revenue.

### Average Ticket Price and Weekly Gross Revenue:
Model,

Though this graph surprised us when we first saw it, after analysis, it makes sense economically. Average ticket prices increasing would increase gross revenue logically. However, at a certain point as price continues increasing, the demand becomes price inelastic, which means the consumers become more reluctant to buy the tickets due to high price, so the seats sold drops, resulting in lower gross revenue at high prices. 

### Percentage of Seats Capacity Sold and Weekly Gross Revenue:
We use geom_point for the visualization of “weekly gross revenue" vs. “percentage of seats capacity sold” and use different colors for different theatre size. The plot reveals the fact that higher percentage of seats capacity sold leads to higher weekly gross revenue. Besides, we find that under same percentage, theatres with larger size will have higher weekly gross revenue. This is the same as we expected, since the total number of seats is higher in larger theatres.

### Number of Performances in the Week and Weekly Gross Revenue:
We then use geom_jitter for the plot of “weekly gross revenue” vs. “number of performances in the week”. However, the graph doesn’t indicate any relationship between them since the data are randomly disbributed without any pattern (that is, theatres with low number of performances per week can have high weekly revenue, while those with high number of performances per week may receive revenue not as high). This is the same for the relationship between “number of performances in the week” and “average ticket price”.

In the next part we focus on factors that affect average ticket price.

### Seat Capacity and Average Ticket Price:
Using the function geom_smooth, all points are joint together to form smooth curves to demonstrate how “average ticket price” is affected by “seat capacity”. From the graph, we can see that there is no relationship between those two variables.

### Conclusion:
...

## Presentation

Our presentation can be found [here](presentation/presentation.html).

## Data 

Hughes, E. & Mock, T. (2018, April 28), Broadway weekly grosses, <https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-04-28>


See http://libraryguides.vu.edu.au/c.php?g=386501&p=4347840 for guidance on proper citation for datasets. 
If you got your data off the web, make sure to note the retrieval date.

## References

List any references here. You should, at a minimum, list your data source.

