---
title: Maximising Profits for Broadway Theatres
author: team
output: github_document
---

```{r, message = FALSE, echo = FALSE}
library(tidyverse)
library(broom)
library(tidytuesdayR)
```

## Summary

Write-up of your project and findings go here. 
Think of this as the text of your presentation. 
The length should be roughly 5 minutes when read out loud.
Although pacing varies, a 5-minute speech is roughly 750 words. 
To use the word count addin, select the text you want to count the words of (probably this is the 
Summary section of this document, go to Addins, and select the `Word count` addin).
This addin counts words using two different algorithms, but the results should be similar and as long as you're in the ballpark of 750 words, you're good! 
The addin will ignore code chunks and only count the words in prose.

You can also load your data here and present any analysis results / plots, but I strongly urge you to keep that to a minimum (maybe only the most important graphic, if you have one you can choose). 
And make sure to hide your code with  `echo = FALSE` unless the point you are trying to make is about the code itself.
Your results with proper output and graphics go in your presentation, this space is for a brief summary of your project.


The dataset used comes from Playbill, which is a US magazine for theatre-goers. The information of weekly box office grosses comes from 'The Broadway League', an association for Broadway theatres. 

There are 47,524 cases of shows that are being played in the theatres at different times in a year.
There are 14 variables. Some of the more important ones which we will be using in our analysis include the following:

1. `show`
2. `theatre`
3. `weekly_gross`
4. `avg_ticket_price`
5. `seats_sold`
6. `seat_capacity`
7. `pct_capacity`
8. `performances`

```{r load-data, echo = FALSE}
grosses <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-28/grosses.csv', guess_max = 40000)
glimpse(grosses)
```

## Presentation
#why mutate

grosses%>%
  ggplot(aes(x=seats_in_theatre))+
  geom_density()

  
#mutate

grosses_2<-grosses%>%
  mutate(theatre_size=(case_when(
    seats_in_theatre<750 ~"small",
    seats_in_theatre<1300 & seats_in_theatre>750 ~"median",
    seats_in_theatre>1299 ~"large")
  )
  )

Our presentation can be found [here](presentation/presentation.html).

## Data 

Hughes, E. & Mock, T. (2018, April 28), Broadway weekly grosses, <https://github.com/rfordatascience/tidytuesday/blob/master/data/2020/2020-04-28>


See http://libraryguides.vu.edu.au/c.php?g=386501&p=4347840 for guidance on proper citation for datasets. 
If you got your data off the web, make sure to note the retrieval date.

## References

List any references here. You should, at a minimum, list your data source.

