---
title: "Project proposal"
author: "team"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(tidytuesdayR)
```

```{r read-grosses, message = FALSE}
grosses <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-28/grosses.csv', guess_max = 40000)

```

*For instructions on what each section should include, please see the [project page](https://idsed.digital/assessments/project/#proposal) on the course website. Remove this text when completing your proposal*.

## 1. Introduction

General Research Question: How to maximise gross weekly revenue in a Broadway show?

The dataset used comes from Playbill, which is a US magazine for theatre-goers. The information of weekly box office grosses comes from 'The Broadway League', an association for Broadway theatres. 

There are 47,524 cases of shows that are being played in the theatres at different times in a year.

There are 14 variables. Some of the more important ones which we will be using in our analysis include the following:

1. `show`
2. `theatre`
3. `weekly_gross`
4. `avg_ticket_price`
5. `seats_sold`
6. `seat_capacity`
7. `performances`

## 2. Data

```{r glimpse-file}
glimpse(grosses)
```


## 3. Data analysis plan

In general, we set "weekly gross revenue" as the response Y, "average ticket price", "seats sold", and "number of performances per week" as the corresponding X. 
For further analysis, we consider "average ticket price" as the response Y,  "seat capacity", "name of theater", "number of week being run" as the corresponding X, to more specifically figure out how each factors contribute to maximize weekly gross revenue.

Our hypotheses are: Higher "average ticket price", "seats sold", and "number of performances per week" lead to higher "gross weekly revenue". More specifically, higher "seat capacity" and "number of week being run" can lead to higher "average ticket price", and the type of "theater" matters as well.


