---
title: "Project proposal"
author: "team"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r load-packages, message = FALSE}
library(tidyverse)
library(broom)
library(tidytuesdayR)
```

```{r read-grosses, message = FALSE}
grosses <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-04-28/grosses.csv', guess_max = 40000)
```

## 1. Introduction

General Research Question: How to maximise gross weekly revenue in a Broadway show?

The dataset used comes from Playbill, which is a US magazine for theatre-goers. The information of weekly box office grosses comes from 'The Broadway League', an association for Broadway theatres. 

There are 47,524 cases of shows that are being played in the theatres at different times in a year.

There are 14 variables. Some of the more important ones which we will be using in our analysis include the following:

1. `show`
2. `theatre`
3. `weekly_gross`
4. `avg_ticket_price`
5. `seats_sold`
6. `seat_capacity`
7. `pct_capacity`
8. `performances`

## 2. Data

```{r glimpse-file}
glimpse(grosses)
```


## 3. Data analysis plan

We set "weekly gross revenue" as the response Y, "average ticket price", "seats sold", and "number of performances per week" as the corresponding X. 
For further analysis, we consider "average ticket price" as the response Y,  "seat capacity", "name of theater", "number of weeks being run" as the corresponding X, to more specifically figure out how each factors contribute to maximize weekly gross revenue.

Our hypotheses are: 

1. Higher "average ticket price", "percentage seats capacity","seats sold", and "number of performances per week" lead to higher "gross weekly revenue."

2. More specifically, higher "seat capacity" and "number of week being run" can lead to higher "average ticket price", and the type of "theater" matters as well.

We will use inferential statistics method which helps show relationship and tendency of data. R visualization will help show the relationship and tendency.For example, to visualize the relation between "average ticket price" and "gross weekly revenue", we use code:

```{r code_preliminary_1,message=FALSE}
grosses%>%
  ggplot(aes(y=weekly_gross,x=avg_ticket_price))+
  geom_smooth()+
  labs(title = "Relationship Between Average Ticket Price and Gross Weekly Revenue",
       x="Average Ticket Price",
       y="Gross Weekly Revenue")
```

In the first preliminary visualization, we get a curve which increases first but decreases after price of 350. We are going to explore the reason that causes the decrease later. 

```{r code_preliminary_2,message=FALSE}
grosses%>%
  ggplot(aes(x=pct_capacity, y=avg_ticket_price))+
  geom_smooth()+
  labs(
    title="Influence of Theatre Seats Sold Percent",
    x="Percent of Theatre Seats Sold",
    y="Average Ticket Price"
       )
```

In the second preliminary visualization, we get a curve with an increasing trend which implies higher percent of theatre seats sold causes higher average ticket price.

```{r code_preliminary_3,message=FALSE}
preliminary_analysis<-grosses%>%
  summarise(mean_avg_price=mean(avg_ticket_price),
            median_avg_price=median(avg_ticket_price),
            max_avg_price=max(avg_ticket_price),
            min_avg_price=min(avg_ticket_price))%>%
  print()
```

In the third preliminary analysis, we analyzed median, average, maximum and minimum of average ticket price.

```{r code_preliminary_4,message=FALSE}
table_theatre<-table(grosses$theatre)
theatre_dataframe<-as.data.frame.array(table_theatre)%>%
  print()
```

In the forth preliminary analysis, we analyzed the different theatres and their frequency.

With the previous preliminary analysis, we found that there are a bulk of different theatres with different seat capacity; percent sold of seat capacity impacts average ticket price. The size of a theatre might be a variable which influences the relationship between percent sold of seat capacity and average ticket price. Hence, we are going to mutate the theatres into different categories by size and do a visualization to explore the relationship further.

Moreover, we are going to create a new column which shows how long each show in runs in each theatre, by using the "mutate" function.

To support our hypothesis, as mentioned previously, we have to draw graphs of the variables in the hypothesis correspondingly -- the positive correlation supports the hypothesis.
