---
title: "Maximising Profits for Broadway Theatres"
#subtitle: <font size='6'>Presentation subtitle (if any)</font>
author: <font size='8'>team <br> Felix, Jeni, Janet</font>
institute: <font size='10'>University of Edinburgh</font>
date: <font size = '6'>`r Sys.Date()`</font>
output:
  revealjs::revealjs_presentation:
    self_contained: false
editor_options: 
  chunk_output_type: console
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(rmarkdown)
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(revealjs)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Load your data here
setwd("/cloud/project/")
grosses <- read_csv("data/grosses.csv")
```

# Dataset

- Tidy Tuesday project file
- Compiled from Playbill, a magazine for theatres
- Information on weekly grosses, average ticket price, etc of different theatre shows
- 14 variables, 47,524 observations

# Dataset 

```{r data}
glimpse(grosses)
```

# Research Question 

<ol>
<li> What are the factors that can affect the average ticket price of a show? </li>
<li> <b> Hence, how does average ticket price then influence the weekly gross revenue earned? </b> </li> 
</ol>

# Gross Weekly Revenue

```{r weekly-gross-frequency, warning = FALSE, message = FALSE, echo = FALSE}
grosses %>% 
  ggplot(aes(x = weekly_gross)) + 
  geom_histogram() +
  labs(
    title = "Frequency of Theatres by Weekly Gross Revenue",
    x = "Weekly Gross Revenue ($)", 
    y = "Frequency",
    fill = "Size of Theatre"
  ) +
  scale_x_continuous(labels = label_dollar(suffix = "M", scale = 1e-6)) 
```

# MUTATE Theatre Size

<ul> 
  <li> less than 750 seats = small </li>
  <li> 750 ~ 1300 = medium </li>
  <li> more than 1300 = large </li> 
</ul>
```{r density-theatre-size, message = FALSE, warning = FALSE, echo = FALSE}
ggplot(grosses, aes(x = seats_in_theatre)) +
  geom_density() +
  labs(x = "Seats in Theatre", y = "Density")
```

```{r mutate-theatre-size, message = FALSE, warning = FALSE, echo = FALSE}
grosses_size <- grosses %>%
  mutate(theatre_size = (case_when(
    seats_in_theatre < 750 ~ "small",
    seats_in_theatre < 1300 & seats_in_theatre > 750 ~ "medium",
    seats_in_theatre > 1299 ~ "large")
  )
  )
```
</div>
</div>

# Gross Weekly Revenue

```{r weekly-gross-frequency-theatre-size, warning = FALSE, message = FALSE, echo = FALSE}
grosses_size %>% 
  filter(theatre_size != is.na(theatre_size)) %>%
  ggplot(aes(x = weekly_gross, fill = theatre_size)) + 
  geom_histogram() +
  labs(
    title = "Frequency of Theatres by Weekly Gross Revenue",
    x = "Weekly Gross Revenue ($)", 
    y = "Frequency",
    fill = "Size of Theatre"
  ) +
  scale_x_continuous(labels = label_dollar(suffix = "M", scale = 1e-6)) 
```

# Percentage Capacity vs Weekly Gross

```{r counting, warning = FALSE, message = FALSE, echo = FALSE}
counting <- grosses_size %>%
  mutate(theatre_show = paste0(theatre, show)) %>%
  group_by(theatre_show) %>%
  mutate(week_running = n())
```

```{r summary-stats, warning = FALSE, message = FALSE, echo = FALSE}
week_running_improved <- counting %>%
  summarise(avg_ticket_price, theatre_show, week_running)

improved <- aggregate(data = week_running_improved,
            week_running_improved$avg_ticket_price,
            by = list(theatre_show = week_running_improved$theatre_show,
                    week_running = week_running_improved$week_running), 
            FUN = mean)
```

```{r pctcapacity-weeklygross, warning = FALSE, message = FALSE, echo = FALSE}
counting %>% 
  ggplot(aes(x = pct_capacity, y = weekly_gross, color = theatre_size)) + 
  geom_point(alpha = 0.5) +
  labs(title = "Percentage of Seats Capacity Sold and Weekly Gross Revenue", 
       y = "Weekly Gross Revenue", 
       x = "Percentage of Seats Capacity Sold",
       color = "Theatre Size") +
  scale_y_continuous(labels = label_dollar(suffix = "M", scale = 1e-6))
```

<p style="font-size:20px"># Main Question: Average Price vs Weekly Gross </p>

```{r avg-price-weekly-gross1, message = FALSE, warning = FALSE, cache = TRUE}
grosses %>%
  ggplot(aes(y = weekly_gross,x = avg_ticket_price)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(title = "Relationship Between Average Ticket Price and Gross Weekly Revenue",
       x = "Average Ticket Price",
       y = "Gross Weekly Revenue") +
  scale_y_continuous(labels = label_dollar(suffix = "M", scale = 1e-6))
```

<p style="font-family:verdana">This is a paragraph.</p>

# Weekly Gross VS. Average Ticket Price Log Model
```{r log_graph,message=FALSE,warning=FALSE}
grosses_log <- grosses%>%
  summarise(
    price_log = log(avg_ticket_price + 0.00001),
    gross_log = log(weekly_gross + 0.00001)
  )

grosses_log%>%
  ggplot(aes(x=price_log, y=gross_log))+
  geom_point()+
  geom_smooth()+
  labs(title = "Log(Weekly Gross) VS. Log(Average Ticket Price)",
       x = "Log(Average Ticket Price)",
       y = "Log(Weekly Gross)")
```

```{r log_model,message=FALSE,warning=FALSE}
logxy_preliminary <-
  linear_reg()%>%
  set_engine("lm")

logxy <- logxy_preliminary %>%
  fit(gross_log ~ price_log, data=grosses_log)
```

```{r test_train_fit,message=FALSE,warning=FALSE}
set.seed(11)
grosses_split<-initial_split(grosses_log,prop = 0.8)
train_data <- training(grosses_split)
test_data <- testing(grosses_split)
grosses_rec <- recipe(gross_log ~.,data = grosses_log)%>%
  step_zv(all_predictors())
grosses_workflow <- workflow()%>%
  add_model(logxy_preliminary)%>%
  add_recipe(grosses_rec)
gross_fit<-grosses_workflow%>%
  fit(data = train_data)
```

```{r pred,message=FALSE,warning=FALSE}
gross_pred<-predict(object = gross_fit, new_data = train_data)%>%
  bind_cols(train_data%>%select(gross_log,price_log))
test_pred<- predict(gross_fit, test_data)%>%
  bind_cols(test_data%>%select(gross_log,price_log))
```

```{r rsq&rmse,message=FALSE,warning=FALSE}
rsq(gross_pred, truth = gross_log, estimate = .pred)
rmse(gross_pred, truth = gross_log, estimate = .pred)
rsq(test_pred, truth = gross_log, estimate = .pred)
rmse(test_pred, truth = gross_log, estimate = .pred)
```   
## reveal.js

- The presentation is created using the `reveal.js` package

- You can create a slide show broken up into sections by using the # and ## heading tags

- You can also create a new slide without a header using a horizontal rule (----)

----

- You can also add pauses between content on a slide using (". . .")

. . .

Like this.

...or using "::: fragment"

::: fragment

Like this.

:::

# Layouts

You can use plain text

- or bullet points

<div>
  <div style="float: left; width: 50%;">or text in two columns</div>
  <div style="float: left; width: 50%;">like this</div>
</div>

because you can combine HTML and Markdown syntax.

<p style="font-size: 8pt; position: absolute; bottom: -5em; width: 100%; text-align: center;">*You can also add footnotes</p>

# Code

# Plots

```{r recode-species, echo = FALSE}
# In this chunk I'm doing a bunch of analysis that I don't want to present 
# in my slides. But I need the resulting data frame for a plot I want to present.
iris_modified <- iris %>%
  mutate(Species = fct_other(Species, keep = "setosa"))
```

```{r plot-iris, echo = FALSE}
# Code hidden with echo = FALSE
# Uses modified iris dataset from previous chunk
# Play around with height and width until you're happy with the look
ggplot(data = iris_modified, mapping = aes(x = Sepal.Width, y = Sepal.Length, color = Species)) +
  geom_point() + 
  theme_minimal() # theme options: https://ggplot2.tidyverse.org/reference/ggtheme.html
```

## Plot and text

::: columns
:::: column
* Some text
* goes here
::::

:::: column
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
::::
:::

## Different widths

::: columns
:::: {.column width="40%"}
* Some text
* goes here
::::

:::: {.column width="60%"}
```{r warning=FALSE, out.width="100%", fig.width=4, echo=FALSE}
# see how I changed out.width and fig.width from defaults
# to make the figure bigger
ggplot(penguins, aes(x = bill_length_mm, y = species, color = species)) +
  geom_boxplot() +
  theme_minimal()
```
::::
:::

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r iris-table, echo = FALSE}
kable(head(iris), format = "html")
```

# Images

```{r castle, echo = FALSE, out.width = "60%", fig.align = "center", fig.cap = "Image credit: Photo by Jörg Angeli on Unsplash."}
include_graphics("https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80")
```

Or you can also include a full page image. See next slide.

## {data-background-image="https://images.unsplash.com/photo-1535448033526-c0e85c9e6968?ixlib=rb-1.2.1&ixid=eyJhcHBfaWQiOjEyMDd9&auto=format&fit=crop&w=1650&q=80"}

# Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs (\$...\$), e.g. $\alpha+\beta$. You can use the display style with double dollar signs:

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

# Feeling adventurous?

You can learn more about the options available at the following pages:

- https://github.com/rstudio/revealjs

- https://bookdown.org/yihui/rmarkdown/revealjs.html

- http://www.jenniferbradham.org/post/reveal_js_markdown/

- https://revealjs.com/