---
title: "Maximising Profits for Broadway Theatres"
#subtitle: <font size='6'>Presentation subtitle (if any)</font>
author: <font size='8'>team <br> Felix, Jeni, Janet</font>
institute: <font size='10'>University of Edinburgh</font>
date: <font size = '6'>`r Sys.Date()`</font>
output:
  revealjs::revealjs_presentation:
    self_contained: false
editor_options: 
  chunk_output_type: console
---

```{r load-packages, include = FALSE}
# Add any additional packages you need to this chunk
library(rmarkdown)
library(tidyverse)
library(tidymodels)
library(palmerpenguins)
library(knitr)
library(revealjs)
```

```{r setup, include=FALSE}
# For better figure resolution
knitr::opts_chunk$set(fig.retina = 3, dpi = 300, fig.width = 6, fig.asp = 0.618, out.width = "80%")
```

```{r load-data, include=FALSE}
# Load your data here
setwd("/cloud/project/")
grosses <- read_csv("data/grosses.csv")
```

# Dataset

- Tidy Tuesday project file
- Compiled from Playbill, a magazine for theatres
- Information on weekly grosses, average ticket price, etc of different theatre shows
- 14 variables, 47,524 observations
- `weekly_gross`, `avg_ticket_price`, `seats_sold`, `seats_in_theatre`, `pct_capacity`, `performances`

# Dataset 

```{r data}
glimpse(grosses)
```

# Research Question 

<ol>
<li> What are the factors that can affect the average ticket price of a show? </li>
<li> <b> Hence, how does average ticket price then influence the weekly gross revenue earned? </b> </li> 
</ol>

## Gross Weekly Revenue

```{r weekly-gross-frequency, warning = FALSE, message = FALSE, echo = FALSE}
grosses %>% 
  ggplot(aes(x = weekly_gross)) + 
  geom_histogram() +
  labs(
    title = "Frequency of Theatres by Weekly Gross Revenue",
    x = "Weekly Gross Revenue ($)", 
    y = "Frequency",
    fill = "Size of Theatre"
  ) +
  scale_x_continuous(labels = label_dollar(suffix = "M", scale = 1e-6)) 
```

## MUTATE Theatre Size
<font size='8'>
  less than 750 seats = small, 750 ~ 1300 = medium, more than 1300 = large
</font>
```{r density-theatre-size, message = FALSE, warning = FALSE, echo = FALSE}
ggplot(grosses, aes(x = seats_in_theatre)) +
  geom_density() +
  labs(x = "Seats in Theatre", y = "Density")
```

```{r mutate-theatre-size, message = FALSE, warning = FALSE, echo = FALSE}
grosses_size <- grosses %>%
  mutate(theatre_size = (case_when(
    seats_in_theatre < 750 ~ "small",
    seats_in_theatre < 1300 & seats_in_theatre > 750 ~ "medium",
    seats_in_theatre > 1299 ~ "large")
  )
  )
```

## Gross Weekly Revenue

```{r weekly-gross-frequency-theatre-size, warning = FALSE, message = FALSE, echo = FALSE}
grosses_size %>% 
  filter(theatre_size != is.na(theatre_size)) %>%
  ggplot(aes(x = weekly_gross, fill = theatre_size)) + 
  geom_histogram() +
  labs(
    title = "Frequency of Theatres by Weekly Gross Revenue",
    subtitle = "coloured by theatre sizes",
    x = "Weekly Gross Revenue ($)", 
    y = "Frequency",
    fill = "Size of Theatre"
  ) +
  scale_x_continuous(labels = label_dollar(suffix = "M", scale = 1e-6)) 
```

## Percentage Capacity

```{r counting, warning = FALSE, message = FALSE, echo = FALSE}
counting <- grosses_size %>%
  mutate(theatre_show = paste0(theatre, show)) %>%
  group_by(theatre_show) %>%
  mutate(week_running = n())
```

```{r summary-stats, warning = FALSE, message = FALSE, echo = FALSE}
week_running_improved <- counting %>%
  summarise(avg_ticket_price, theatre_show, week_running)

improved <- aggregate(data = week_running_improved,
            week_running_improved$avg_ticket_price,
            by = list(theatre_show = week_running_improved$theatre_show,
                    week_running = week_running_improved$week_running), 
            FUN = mean)
```

```{r pctcapacity-weeklygross, warning = FALSE, message = FALSE, echo = FALSE}
grosses_size %>% 
  filter(theatre_size != is.na(theatre_size)) %>% 
  ggplot(aes(x = pct_capacity, y = weekly_gross, color = theatre_size)) + 
  geom_point(alpha = 0.5) +
  labs(title = "Percentage of Seats Capacity Sold and Weekly Gross Revenue", 
       y = "Weekly Gross Revenue", 
       x = "Percentage of Seats Capacity Sold",
       color = "Theatre Size") +
  scale_y_continuous(labels = label_dollar(suffix = "M", scale = 1e-6))
```

## Week Running
```{r total-weeks-revenue, message = FALSE, warning = FALSE, echo = FALSE}
counting %>%
  ggplot(aes(x = week_running, y = weekly_gross))+
  geom_point()+
  labs(x = "Weeks Running", y = "Weekly Gross Revenue",
       title = "Week Running of Show vs Weekly Gross Revenue")+
  scale_y_continuous(labels = label_dollar(suffix = "M", scale = 1e-6))
```

## Number of Performances Per Week 
```{r performances-per-wk-revenue, message = FALSE, warning = FALSE, echo = FALSE}
grosses %>%
  ggplot(aes(x = performances, y = weekly_gross))+
  geom_point()+
  labs(x = "Number of Performances Per Week", y = "Weekly Gross Revenue",
       title = "Number of Performances Per Week")+
  scale_y_continuous(labels = label_dollar(suffix = "M", scale = 1e-6))
```

## Main Research
```{r main-question, message = FALSE, warning = FALSE, echo = FALSE, cache = TRUE}
grosses %>%
  ggplot(aes(y = weekly_gross,x = avg_ticket_price)) +
  geom_point() +
  geom_smooth(se = FALSE) +
  labs(title = "Average Ticket Price vs Weekly Gross Revenue",
       x = "Average Ticket Price",
       y = "Weekly Gross Revenue") +
  scale_y_continuous(labels = label_dollar(suffix = "M", scale = 1e-6))
```

## Average Ticket Price vs Seats Sold
```{r seats-sold-vs-avg-price, message = FALSE, warning = FALSE, echo = FALSE}
seats_df <- grosses %>%
  filter(avg_ticket_price > 400)

grosses %>%
  ggplot(aes(x = avg_ticket_price, y = seats_sold)) + 
  geom_point() +
  geom_point(data = seats_df, 
             aes(x = avg_ticket_price, y = seats_sold), 
             colour = "red") +
  labs(title = "Average Ticket Price vs Seats Sold",
       x = "Average Ticket Price",
       y = "Seats Sold")
```

## The Log Model
```{r log-graph,message = FALSE,warning = FALSE, echo = FALSE}
grosses_log <- grosses%>%
  summarise(
    price_log = log(avg_ticket_price + 0.00001),
    gross_log = log(weekly_gross + 0.00001)
  )

grosses_log%>%
  ggplot(aes(x=price_log, y=gross_log))+
  geom_point()+
  geom_smooth()+
  labs(title = "Log(Weekly Gross) VS. Log(Average Ticket Price)",
       x = "Log(Average Ticket Price)",
       y = "Log(Weekly Gross)")
```

## Set Model
```{r log-model, message=FALSE, warning=FALSE}
logxy_preliminary <-
  linear_reg() %>%
  set_engine("lm")

logxy <- logxy_preliminary %>%
  fit(gross_log ~ price_log, data = grosses_log)
```
$$y=e^{6.81}x^{1.51}$$
```{r test-train-fit, message = FALSE, warning = FALSE,echo=FALSE}
set.seed(11)
grosses_split <- initial_split(grosses_log, prop = 0.8)
train_data <- training(grosses_split)
test_data <- testing(grosses_split)
grosses_rec <- recipe(gross_log ~.,data = grosses_log)

grosses_workflow <- workflow() %>%
  add_model(logxy_preliminary) %>%
  add_recipe(grosses_rec)

gross_fit <- grosses_workflow %>%
  fit(data = train_data)
```
```{r pred, message = FALSE,warning = FALSE,echo=FALSE}
gross_pred <- predict(object = gross_fit, new_data = train_data) %>%
  bind_cols(train_data %>% select(gross_log, price_log))
test_pred <- predict(gross_fit, test_data) %>%
  bind_cols(test_data %>% select(gross_log,price_log))
```
## R Squared and RMSE
```{r rsq-rmse,message=FALSE,warning=FALSE,echo=FALSE,echo=FALSE}
rsq(gross_pred, truth = gross_log, estimate = .pred)
rmse(gross_pred, truth = gross_log, estimate = .pred)
rsq(test_pred, truth = gross_log, estimate = .pred)
rmse(test_pred, truth = gross_log, estimate = .pred)
```   
## RSQ-RMSE Table & Cross Validation
```{r,message=FALSE,warning=FALSE,echo=FALSE}
test_train_table <- tribble(
  ~Pred, ~RSQ, ~RMSE,
  "Test Data", 0.910, 0.451,
  "Train Data", 0.913, 0.445,
)
knitr::kable(head(test_train_table),"html")
```
```{r,message=FALSE,warning=FALSE,echo=FALSE}
set.seed(20)
folds <- vfold_cv(train_data,v=5)
fit_rs <- grosses_workflow%>%
  fit_resamples(folds)
collect_metrics(fit_rs)
collect_metrics(fit_rs, summarize = FALSE)%>%
  summary()
```

## Equation & Graph
$$y=e^{6.81}x^{1.51}$$
```{r log curve,message=FALSE,warning=FALSE,echo=FALSE}
curve((2.71828182846)^6.81*x^1.51,from = 0, to = 500, 
      xlab="Average Ticket Price", 
      ylab="Weekly Gross")
```

## Conclusion
- theatre size, percentage capacity, average price influenced weekly gross 
- number of performances per week, total number of weeks show ran for did not
- modelled relationship between average ticket price and weekly gross revenue, which was found to be positive 

## Limitations & Extensions
- Limitations: might only be a particular set of customers in Broadway, larger samples of data

- Future Extension: model that can include the exponential curvature of the graph

# Thank you for watching
